% //home/mark/cv/frontend/public/assets/Ibrahim_Al-Asfar_CV.tex

% Setting up document class and essential packages
\documentclass[a4paper,11pt]{article}
\usepackage{geometry}
\geometry{left=2cm,right=2cm,top=2cm,bottom=2cm}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[arabic,english]{babel}
\usepackage{noto}

% Customizing section titles
\titleformat{\section}{\large\bfseries\color{blue}}{\thesection}{1em}{}
\setlength{\parskip}{0.5em}
\setlist[itemize]{leftmargin=1.5cm}

% Document content
\begin{document}

% Adding personal information in a centered header
\begin{center}
    {\LARGE\bfseries Ibrahim Maged Mohamed Al-Asfar} \\[0.5em]
    \hrulefill \\[0.5em]
    Phone: \href{tel:+201212444617}{+20 1212444617} \quad | \quad 
    Email: \href{mailto:marklasfar@gmail.com}{marklasfar@gmail.com} \\
    Address: Zagazig, Sharqia, Egypt \quad | \quad 
    Date of Birth: 11 April 1999 \\
    GitHub: \href{https://github.com/Mark-Lasfar}{github.com/Mark-Lasfar}
\end{center}

% Defining career objective with aspirations for MGZon AI
\section*{Career Objective}
Passionate Full Stack Web Developer and founder of MGZon AI, an AI-driven global e-commerce platform inspired by Amazon and Shopify. MGZon AI provides personalized shopping experiences and dedicated vendor stores, targeting international markets with integrations for payment, warehousing, dropshipping, and marketing. With over 5 years of programming experience, I specialize in TypeScript, MongoDB, React, Django, and Linux systems. I aim to establish MGZon AI as a leading e-commerce fleet, currently working on registering it as a U.S.-based company. My skills in client acquisition, persuasive communication, and strategic planning drive high sales and profitability.

% Listing educational background
\section*{Education}
\textbf{Bachelor of Information Systems} \hfill 2020--2023 \\
Faculty of Computers and Information, Alexandria University, Egypt \\
Grade: Very Good

% Detailing professional experience
\section*{Work Experience}
\textbf{Founder \& Lead Developer, MGZon AI} \hfill 2023--Present
\begin{itemize}
    \item Founded MGZon AI, a next-generation e-commerce platform with AI-driven personalization, operating under U.S. licenses and targeting global markets.
    \item Developed scalable systems for vendors, users, and suppliers, integrating payment gateways, warehousing (U.S., Canada, China), dropshipping, and marketing solutions.
    \item Built robust backend infrastructure using TypeScript, MongoDB, and Django, emphasizing scalability, user experience, and complex project management.
\end{itemize}

\textbf{Freelance Developer (Remote)} \hfill 2020--2023
\begin{itemize}
    \item Developed e-commerce platforms with API integrations for multiple gateways, focusing on scalability and efficiency.
    \item Utilized Linux systems and terminal-based workflows for development, deployment, and optimization.
    \item Demonstrated strong client acquisition skills, driving sales through persuasive communication and strategic planning.
\end{itemize}

\textbf{Unpaid Internship, USBank (Online)} \hfill 2022
\begin{itemize}
    \item Gained experience in financial systems and online banking operations.
    \item Collaborated on API integrations and system testing in a remote environment.
\end{itemize}

% Outlining technical and soft skills
\section*{Skills}
\begin{itemize}
    \item \textbf{Technical Skills:}
    \begin{itemize}
        \item Programming: HTML5, CSS3, JavaScript, TypeScript, Python, PHP
        \item Frameworks \& Libraries: React, Node.js, Django
        \item Databases: MongoDB, PostgreSQL, SQL
        \item Tools \& Technologies: Git, Docker, Linux, Terminal-Based Workflows
        \item Design: UX/UI Design, API Integration
        \item Other: Complex Project Planning, Search Engine Optimization (SEO)
    \end{itemize}
    \item \textbf{Soft Skills:}
    \begin{itemize}
        \item Strategic planning and goal-oriented problem-solving
        \item Persuasive communication and client acquisition
        \item Teamwork and collaboration under pressure
        \item Strong time management and complex project handling
    \end{itemize}
\end{itemize}

% Listing relevant training and certifications
\section*{Training \& Courses}
\begin{itemize}
    \item FreeCodeCamp: Web Development and JavaScript Certifications
    \item Online Courses: Python, React, TypeScript
    \item Unpaid Internship: USBank (Online)
\end{itemize}

% Highlighting GitHub contributions
\section*{GitHub Achievements}
\begin{itemize}
    \item Pull Shark: Significant contributions to open-source projects
    \item YOLO: Pushed commits without review
    \item Quickdraw: Rapid pull request resolutions
\end{itemize}

% Specifying language proficiency
\section*{Languages}
\begin{itemize}
    \item Arabic: Native
    \item English: Intermediate
\end{itemize}

% Including a motivational quote
\section*{Favorite Quote}
\begin{quote}
If you want to set a goal, set it at the stars. Because even if you lose this goal, you will definitely reach the moon. Motivate yourself constantly because you deserve to be the best.
\end{quote}

\end{document}